---
title: 'Assignment 2 - Preliminary Report'
subtitle: 'Setting the environment'
author: "Sharon Van Den Berg"
date: "2025-03-24"

knit: (function(input, encoding) {
  rmarkdown::render(input,
                    encoding = "UTF-8",
                    output_dir = "../report",
                    knit_root_dir = rprojroot::find_rstudio_root_file())})
                    
output: 
  #html_document:
  pdf_document:
    includes:
      in_header: import.sty
      before_body: title.sty
      #after_body: tail.sty
      toc: yes
      keep_tex: yes
      number_sections: yes
geometry: margin= 2.00cm
font-size: 11pt
font-style: "Times New Roman"
line-spacing: 1.5
header-includes:
  #Use the package setspace to use 1 and a half line spacing for readability
  #Other option could be \doublespacing to have 2 lines between writing
  - \usepackage{setspace}
  - \onehalfspacing

bibliography: DSAA811_prelim.bib
link-citations: TRUE
citation_package: apa-annotated.csl
---

````{=html}
<!--
```{=tex}
\begin{center}
{\Large{School of Mathematics \& Applied Statistics}}\\[10pt]
{\LARGE{\bf{DSAA311/DSAA811: Data Analytics and Visualisation}}} \\[10pt]
{\Large{\bf{Preliminary Report}}}\\[10pt]
\end{center}
\newpage
```
-->
````

```{r setup, include=FALSE}
library(knitr)
library(tinytex)
library(tidyverse)
opts_chunk$set(echo = TRUE)
```

\newpage

# Abstract

```{r child = 'src/abstract.Rmd'}
```


```{=tex}
  %Display the table of contents and bypass the R commands to do this
  \newpage
  \tableofcontents
\newpage
```

# Introduction

```{r child = 'src/introduction.Rmd'}
```


# Background

# Research questions and aims of the project

# Rationale

# Data Description

# Exploritory data analysis

# Conclusion

For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

```{r cars}
summary(cars)
```

```{r pressure, echo=FALSE}
plot(pressure)
```

\newpage

#Session Information

```{r sessionInfo}
sessionInfo()
```

\newpage
# Bibliography